\chapter{Scripts by Telair}%
\label{cha:scripts}

\footnotetext[1]{\fullref{part:location_scripts}}
\footnotetext[2]{\fullref{part:location_finalimage}}

Some helper scripts exists, written by Telair International GmbH to make working
with PTXDist and usage easier for the user in kind of building kernel and
software as also to build up a bootable sdCard. All the scripts you will find in
the tools telair folder~\footnotemark[1].

\section{Build a bootable image }%
\label{sec:build_image_script}
To build a howl --- ready to use --- image with predefined partions and pre
installed software and content use the script.

\begin{itemize}
    \item   sdCard\_generateFlashableImagefile.sh
\end{itemize}

It will generate an image into the image directory~\footnotemark[2].

This image can be copied directly to the SDCard. You can therefore the
script below or an other tool which is able to copy block wise bootable images
to devices. For example like:

\begin{description}
    \item[Linux] Linux standard Tool dd. See \textit{man 1 dd}. For example
        dd if=<youImage> of=<yourDevice> bs=1M status=progress
\item[Windows] Use WinImage. See~\cite{win32DiskImager}
\end{description}


\section{Copy an Image from/to SD Cards}%
\label{sec:sdCard_flashImage}
An script is available~\footnotemark[1] to copie (flashes) an Image file to an
SD Card.

\begin{itemize}
    \item sdCard\_installImage.sh
\end{itemize}


\section{Partion am SD Card}%\label{cha:partion_script}
To build a empty bootable SDCard with four partions (boot, rootFS, data, log).
This is only needed if you like to build the SDCard from scratch. Use the
therefor the script located in telair tools directory~\footnotemark[1] called:
\begin{itemize}
    \item   sdCard\_createPartions.sh
\end{itemize}

If you can afterwards fill up the partions by a script below.


\section{Fill up the SD Card}%\label{part:copyfiles_script}
    To add (install) all needed files to the right partions and locations
    on a preformated bootable sdCard (applications, kernel, bootloaer, data,
    others) use the script~\footnotemark[1]:
\begin{itemize}
    \item sdCard\_fillupPartions.sh
\end{itemize}

\section{Build All}%
\label{sec:build_all}
An script (wrapper to PTXDist and telair scripts) exists, which recompiles the
CP\_760790 Software for you and builds finally an ready to flash image file
\footnotemark[1].
\begin{itemize}
    \item telair\_buildAll.sh
\end{itemize}

Optional this script can copy also the image on an SDCard if exists.
