\chapter{The CP790760 Software}%
\label{cha:software}
The QT4 based Software cargo control software by Telair International GmbH was
taken from the original previous project. Beside some
changes~\ref{sec:software_changes} the software was left untouched.

\section{Software documentation}%
\label{sec:Software_documentation}
This document holds no documentation about the software itself. Documentation
was already preformed by by requirement documentation and is true also for the
software used in this project. No further documentation is needed beside the
software changes in~\ref{sec:software_changes}.


\section{Changes to the Software}%
\label{sec:software_changes}
Mostly the QT4 based Telair Cargo Control Software CP790760 was left untouched.
Nevertheless some changes ware needed to migrate hard coded Linux 3.\@
dependencies to Linux 4.


All changes are preformed by use of C macros inside the original files, whereas
its corespondent values encapsulated into new file inside the software folder.
\footnotemark[1]

\begin{alltt}
    \textbf{<cp790760\_softwareroot>/\textbf{linuxversion\_dependencies.h}}
\end{alltt}

\section{Compliance Check and Code Analyze}%
\label{sec:software_anaylse}

The software \textbf{was} tested against functionality. \textbf{Note, no}
other checks were preformed.

\begin{itemize}
    \item The software \textbf{is not} checked by any code analyze tool against
        (possible) bugs or undefined behavior. For example static code analyze.
    \item The software \textbf{is not} checked by any software compliance tool
        against common coding coding rules and guidelines. For example no MISRA
        or CERT.\@
    \item \textbf{No} code reviews were preformed. For example reviews about
        Security or Safety.
\end{itemize}


\section{How to change the Software}%
\label{sec:software_change}
To edit the software sources, change to the software location inside the PTXdist
project. \footnotemark[1]. There you can edit the
sources with your favorite editor or \glsshortkey{IDE}. The software can be
compiled by PTXdist.

\subsection{Compile the CP790760 Software}%
\label{sub:compile_CP790760}

PTXDist does not check every single file and folder inside your project against
integrity like manual changes. This would be much to time intensive. That is
why you need to inform PTXDist yourself about your changes.

Therefor first change to you <projectroot> directory and run afterwards
\footnotemark[1]:



\bigbreak%
\begin{lstlisting}[caption=Mark the CP790760 software as changed]
user@machine:  ptxdist clean telair-cp_790760_1
\end{lstlisting}

Now you can run a software build manual or wait till PTXdist will preformed it
automatically during next generation of howl system images. To build it manual
run from you <projectroot>

\bigbreak%
\begin{lstlisting}[caption=Build the Telair CP790760 software manual]
user@machine:  ptxdist targetinstall telair-cp_790760_1
\end{lstlisting}


Generation of howl images is described in \fullref{sec:final_images_generation}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\footnotetext[1]{See \fullref{part:location_cp790760_software}}
